### 2023-04-05 reachable-resilience.tex
up

\begin{theorem}
{\sc State-resilience} is undecidable for effective WSTS with  strong  compatibility 
when
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong upward compatibility ~ & $\uparrow post^*$ effective & both  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Corollary~\ref{bsrp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Corollary~\ref{bsrp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable  & Decidable   & Decidable \\ \hline
   BSRP & Undecidable  &  ??  & Decidable \\ \hline
      kSRP & Undecidable  & ?? & Decidable  \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{theorem}\label{srp down up}
{\sc State-resilience} is undecidable for effective WSTS with  strong  compatibility 
when
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong upward compatibility ~ & $\uparrow post^*$ effective & both  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Thm~\ref{srp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Thm~\ref{srp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable   & Decidable \\ \hline
   BSRP & ??  &  ??  & Decidable \\ \hline
      kSRP & ??  & ?? & Decidable  \\ \hline
 \end{tabular}
\end{center}
